title: "smithsionianinternetarchive"
author: "George Oberle"
date: "March 29, 2015"
output: html_document
---

```{r}
library(magrittr)
library(internetarchive)
library(dplyr)
library(tidyr)
 
query <- c("collection" = "smithsonian")
 
smithsonian <- query %>%
ia_search(num_results = 6000) %>%
ia_get_items() %>%
ia_metadata() 
```


```{r}
wide <- smithsonian %>%
  filter(field %in% c("title", "date", "creator", "publisher", "subject1")) %>%
  spread(field, value) %>%
  mutate(date=as.integer(date))
```




```{r}
query_1 <- c("creator" = "peale")
 
american_libraries <- query_1 %>%
ia_search(num_results = 500) %>%
ia_get_items() %>%
ia_metadata() 
```





```{r}
library(mullenMisc)
library(ggplot2)
library(stringr)
library(dplyr)
```


```{r}
marcdata <- read.csv(file = "marc.csv", sep = ",", stringsAsFactors = FALSE)
```





The three steps are (1) get the item ids with ia_search, (2) get the
JSON representation of those items with ia_get_items, and (3) turn
those items into a data frame with ia_metadata.

query1 <- c("title" = "damnation of theron ware")
ia_search(query1)

query1 <- c("collection" = "smithsonian")
items  <- ia_search(query1, num_results = 6000)